\Large \bf One-Step, Three-Factor Authentication with Custom-Fit, In-Ear EEG

### 2017-02-16 paper.tex
minor proofs

\subsection*{Abstract}
In this paper, we present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step by using brain-based authentication via custom-fit, in-ear electroencephalography (EEG). We demonstrate its potential by collecting electroencephalography (EEG) data from seven participants using manufactured custom-fit earpieces with embedded electrodes. Across all participants, we achieve mean 0\% false acceptance and 0.017\% false rejection rates with data from only one earpiece with three electrodes. Furthermore, we find a 0\% false acceptance rate in a preliminary simulation of an impersonation attack. We also report some positive usability perspectives from our participants and discuss constructive directions for future work. Our results indicate that in-ear EEG could provide a discreet, convenient, and usable method for secure one-step, three-factor authentication.

@@

The first quality check was examining the electrical impedances achieved for the ear pieces as a low impedance (<10 kOhm) 
is best for obtaining quality EEG signals. Table \ref{tab:impedances} below summarizes the impedances across the seven participants' six ear channels. With the exception of a few channels in select participants, impedances achieved were overall good. Most of the recorded impedances of the earpiece electrodes were less than 5 k\(\Omega\), a benchmark used widely in previous ear EEG work, and all except two were less than 10 k\(\Omega\). Nonetheless, the data from all electrodes were tested in the remaining two data quality tests.

>>>>

\subsection*{Abstract}
We present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step by using brain-based authentication via custom-fit, in-ear electroencephalography (EEG). We demonstrate its potential by collecting electroencephalography (EEG) data from seven participants using manufactured custom-fit earpieces with embedded electrodes. Across all participants, we achieve mean 0\% false acceptance and 0.017\% false rejection rates with data from only one earpiece with three electrodes. Furthermore, we find a 0\% false acceptance rate in a preliminary simulation of an impersonation attack. We also report some positive usability perspectives from our participants and discuss constructive directions for future work. Our results indicate that in-ear EEG could provide a discreet, convenient, and usable method for secure one-step, three-factor authentication.

@@

The first quality check was examining the electrical impedances achieved for the ear pieces as a low impedance ($<$10 kOhm) 
is best for obtaining quality EEG signals. Table \ref{tab:impedances} below summarizes the impedances across the seven participants' six ear channels. With the exception of a few channels in select participants, impedances achieved were overall good. Most of the recorded impedances of the earpiece electrodes were less than 5 k\(\Omega\), a benchmark used widely in previous ear EEG work, and all except two were less than 10 k\(\Omega\). Nonetheless, the data from all electrodes were tested in the remaining two data quality tests.
